Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-07-29 Masterarbeit_Robotik_Pamuk.tex
pdfs and imgs, robotic application

\chapter{Real-Time Robotic Application}\label{cha:real-time-testing}

\section{VARAN}
\section{Robotic Application}
\clearpage

>>>>

\chapter{Real-Time Robotic Application}\label{cha:real-time-testing}
This chapter compares the latency of the Salamander 4 operating system before and after the real-time performance tunings. Additionally, these results are contrasted with the latency of Salamander 4 running on bare metal hardware to understand how closely the performance of the virtualized system can match that of the bare metal system. The experimental setup includes a six-axis mini-robot, illustrated in figure \ref{fig:mini_robot}.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{img/experiment/mini_robot.jpg}
	\caption[Mini-robot of the experiment]{Mini-robot of the experiment}
	\label{fig:mini_robot}
\end{figure}

\noindent In order to move this robot, it needs to get signals  
The program is written in Lasal Class 2 and will be applied to all three versions to measure the reaction time of the robot to the specific commands.

\ref{fig:hardware_tree}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{img/experiment/hardware_tree.png}
	\caption[Hardware tree]{Hardware tree}
	\label{fig:hardware_tree}
\end{figure}

\ref{fig:virt_tree}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\columnwidth]{img/experiment/virt_tree.png}
	\caption[Virt tree]{Virt tree}
	\label{fig:virt_tree}
\end{figure}

\begin{comment}
	https://www.sigmatek-automation.com/en/products/accessories/controls-hmis/pcv-522/
\end{comment}

\section{Robotic Application}
